New lower bounds for Schur and weak Schur numbers

### 2021-09-23 article/article.tex
removed qquad

\qquad [OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.

\qquad [NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand. As the use of templates
is quite recent, we expect the bounds to be improved by carrying on our work further. For example, one may try to use
algorithms based on randomness such as Monte-Carlo algorithms to find better templates.

@@

\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
us during the whole research and writing. We also would like to address warm thanks
to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
new lower bound for \(\WS(6)\).

>>>>

[OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.

[NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand. As the use of templates
is quite recent, we expect the bounds to be improved by carrying on our work further. For example, one may try to use
algorithms based on randomness such as Monte-Carlo algorithms to find better templates.

@@

We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
us during the whole research and writing. We also would like to address warm thanks
to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
new lower bound for \(\WS(6)\).

### 2021-09-23 article/weakschur.tex
removed qquad

\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
given in this paper.

@@

\qquad Up to now, no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
\cite{AbbottHanson} was known. Here we give a general lower bound for weak Schur numbers as a function of both
regular and weak Schur numbers.

@@

\qquad In this subsection, we introduce WS-templates and prove calculative results for the general construction
theorem on templates for weak Schur numbers.

@@

\begin{proof}[\textsc{Proof.}]
By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
The result is then obtained by simplifying the equality. \\
\end{proof}

@@

Having established these properties, we now have everything we need to state and prove our main result. We proceed to do so
in the next subsection.

>>>>

In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
given in this paper.

@@

Up to now, no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
\cite{AbbottHanson} was known. Here we give a general lower bound for weak Schur numbers as a function of both
regular and weak Schur numbers.

@@

In this subsection, we introduce WS-templates and prove calculative results for the general construction
theorem on templates for weak Schur numbers.

@@

\begin{proof}[\textsc{Proof.}]
By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
The result is then obtained by simplying the equality. \\
\end{proof}

@@

We now proceed to state and prove the main result of this article.
